Addition and removal energies of circular quantum dots

### 2017-09-05 Manuscript/paper.tex
Minor fixes

In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method \cite{hartree_1928,Fock1930}, M\o ller--Plesset perturbation theory (MP) \cite{1934PhRv...46..618M}, the in-medium similarity renormalization group (IM-SRG) method \cite{IMSRG}, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT) \cite{0022-3700-7-18-010,Kvasnicka1974}, and equations-of-motion (EOM) methods \cite{RevModPhys.40.153}.  We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from existing literature.

@@

>>>>

In this paper, we analyze the application of several methods to the quantum dot systems, including the Hartree--Fock (HF) method \cite{hartree_1928,Fock1930}, M\o ller--Plesset (MP) perturbation theory \cite{1934PhRv...46..618M}, the in-medium similarity renormalization group (IM-SRG) method \cite{IMSRG}, coupled cluster (CC) theory \cite{PhysRevB.67.045320,heidari:114708,PhysRevB.84.115302}, quasidegenerate perturbation theory (QDPT) \cite{0022-3700-7-18-010,Kvasnicka1974}, and equations-of-motion (EOM) methods \cite{RevModPhys.40.153,StantonBartlettEOM,EMRICH1981379}.  We compare them against variational and diffusion Monte Carlo (VMC and DMC) \cite{PhysRevB.68.035304,PhysRevB.62.8120,PhysRevB.84.115302,PhysRevB.54.4780} and full configuration interaction (FCI) theory \cite{olsen2013thesis,JJAP.36.3924,PhysRevB.56.6428,2008arXiv0810.2644K,rontani:124102} results, where available, from existing literature.

@@

Lastly, we note that from the above discussion it is clear that the IM-SRG is closely related to several other well-known methods of quantum chemistry such as coupled cluster theory \cite{shavitt2009many}, canonical transformation theory \cite{White:cond-mat0201346,CTreview}, the irreducible (or anti-Hermitian) contracted Schr\"odinger equation approach \cite{Mazzioti1,Mazzioti2}, and the driven similarity renormalization group method \cite{Evangelista}.  We refer the reader to Ref.\ \cite{HeikoReview} for a discussion of similarities with and differences from these approaches.
